---
title: "RWorksheet_Bansara#4c"
author: "Abdul Azim Bansara"
date: "2023-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Use the dataset mpg

1a. Show your solutions on how to import a csv file into the environment.
```{r}

mpgdata <- read.csv("mpg.csv")

```


1b. Which variables from mpg dataset are categorical?
```{r}
str(mpg)




```


1c. Which are continuous variables?
```{r}


```

2. Which manufacturer has the most models in this data set? Which model has the most variations? Show your answer
```{r}
library(ggplot2)


manumodel <- table(mpg$manufacturer)

manumax <- names(which.max(manumodel))

cat("Manufacturer with the most models:", manumax, "\n")


#finding most variations
manumaxdata <- subset(mpg, manufacturer==manumax)
model_counts <- table(manumaxdata$model)

mostvarmod <- names(which.max(model_counts))
cat("Model with the most variations:", mostvarmod, "\n")





```

2a.Group the manufacturers and find the unique models. Show your codes and result.
```{r}
library(ggplot2)
library(dplyr)

manumod <- mpg%>%
  group_by(manufacturer)%>%
  summarize(uniquemodel = n_distinct(model))

print(manumod)



```

2b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}

plot(manumod$manufacturer, manumod$uniquemodel, 
            main = "Unique model per manufacturer",
            xlab = "Manufacturer",
            ylab = "Number of unique models")



#ggplot
library(ggplot2)
ggplot(manumod, aes(x=manufacturer,y = uniquemodel))+
  geom_bar(stat = "Identity",fill = "blue")+
  labs(title = "Unique model per manufacturer",
       x = "Manufacturer",
       y = "Number of unique models")+
  theme_gray()

   


```


2a.What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()

# it shows the points where model and manufacturer are.
-
```



2b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r}
#yes it is useful

```

3.
```{r}
library(ggplot2)

top20 <- head(mpg,20)

ggplot(top20, aes(x = model, y = year))+
  geom_point()+
  labs(title = "Model vs Year(Top 20 observations)",
       x = "Model",
       y= "Year")+
  theme(axis.text.x = element_text(angle = 45,hjust = 1))




```



4.Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}
library(dplyr)
modelgroup <- mpg%>%
  group_by(manufacturer)
 

print(modelgroup)

```



4a.
```{r}


```